---
title: "Test Scores"
author: "Charlotte Lopp"
date: "February 22, 2018"
output: html_document
---

```{r load-libraries, message = FALSE, echo = FALSE}
# load general-use packages
library("dplyr")
library("tidyr")
library("knitr")
library("ggplot2")
library("ggthemes")
library("kableExtra")
library("plyr")
```

```{r setup-training-scores, echo = FALSE}
# This downloads the csv files with our data
# into our project directory
#ten <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-17-0220.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#twenty <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-17-0931.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#thirty <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-18-0228.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#forty <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-18-1732.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#fifty <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-18-2039.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#sixty <- read.csv(paste0("data/",
#                                "Users-Export-2018-February-19-0036.csv"),
#                                header = TRUE,
#                                stringsAsFactors = FALSE)

#use_ten <- subset(ten, select = -c(X_trainings_0_training_score,
#                                   X_trainings_1_training_score,
#                                   X_trainings_2_training_score,
#                                   X_trainings_3_training_score,
#                                   X_trainings_4_training_score,
#                                   X_trainings_5_training_score,
#                                   X_trainings_6_training_score,
#                                   X_trainings_7_training_score,
#                                   X_trainings_8_training_score,
#                                   X_trainings_9_training_score,
#                                   X_trainings_10_training_score))

#use_twenty <- subset(twenty, select = -c(X_trainings_11_training_score,
#                                   X_trainings_12_training_score,
#                                   X_trainings_13_training_score,
#                                   X_trainings_14_training_score,
#                                   X_trainings_15_training_score,
#                                   X_trainings_16_training_score,
#                                   X_trainings_17_training_score,
#                                   X_trainings_18_training_score,
#                                   X_trainings_19_training_score,
#                                   X_trainings_20_training_score))

#use_thirty <- subset(thirty, select = -c(X_trainings_21_training_score,
#                                   X_trainings_22_training_score,
#                                   X_trainings_23_training_score,
#                                   X_trainings_24_training_score,
#                                   X_trainings_25_training_score,
#                                   X_trainings_26_training_score,
#                                   X_trainings_27_training_score,
#                                   X_trainings_28_training_score,
#                                   X_trainings_29_training_score,
#                                   X_trainings_30_training_score))

#use_forty <- subset(forty, select = -c(X_trainings_31_training_score,
#                                   X_trainings_32_training_score,
#                                   X_trainings_33_training_score,
#                                   X_trainings_34_training_score,
#                                   X_trainings_35_training_score,
#                                   X_trainings_36_training_score,
#                                   X_trainings_37_training_score,
#                                   X_trainings_38_training_score,
#                                   X_trainings_39_training_score,
#                                   X_trainings_40_training_score))

#use_fifty <- subset(fifty, select = -c(X_trainings_41_training_score,
#                                   X_trainings_42_training_score,
#                                   X_trainings_43_training_score,
#                                   X_trainings_44_training_score,
#                                   X_trainings_45_training_score,
#                                   X_trainings_46_training_score,
#                                   X_trainings_47_training_score,
#                                   X_trainings_48_training_score,
#                                   X_trainings_49_training_score,
#                                   X_trainings_50_training_score))

#use_sixty <- subset(sixty, select = -c(X_trainings_51_training_score,
#                                   X_trainings_52_training_score,
#                                   X_trainings_53_training_score,
#                                   X_trainings_54_training_score,
#                                   X_trainings_55_training_score,
#                                   X_trainings_56_training_score,
#                                   X_trainings_57_training_score,
#                                   X_trainings_58_training_score,
#                                   X_trainings_59_training_score))
```

```{r setup-training-history, echo = FALSE}
# This downloads the csv files with our data
# into our project directory
FACS <- read.csv(paste0("data/",
                                "FACS-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

SETT <- read.csv(paste0("data/",
                                "SETT-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

METT <- read.csv(paste0("data/",
                                "METT-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

RETT_F <- read.csv(paste0("data/",
                                "RETT-Family-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

RETT_LE <- read.csv(paste0("data/",
                                "RETT-LE-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

RETT_W <- read.csv(paste0("data/",
                                "RETT-Workplace-training-history.csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

data <- read.csv(paste0("data/",
                                "register-2018-02-23 (1).csv"),
                                header = TRUE,
                                stringsAsFactors = FALSE)

use_FACS <- subset(FACS, select = -c(user_login, country, training_id, timespan))

use_SETT <- subset(SETT, select = -c(user_login, country, training_id, timespan))

use_METT <- subset(METT, select = -c(user_login, country, training_id, timespan))

use_RETT_F <- subset(RETT_F, select = -c(user_login, country, training_id, timespan))

use_RETT_LE <- subset(RETT_LE, select = -c(user_login, country, training_id, timespan))

use_RETT_W <- subset(RETT_W, select = -c(user_login, country, training_id, timespan))
```

## Training History of Tools: FACS
```{r FACS, fig.height = 20, fig.width = 22, echo = FALSE}
# This looks at the trend of training tool score
# by customer for FACS
use_FACS$date_taken <- format(as.Date(use_FACS$date_taken), "%m/%d/%y")

FACS_ID <- use_FACS %>%
  group_by(user_id) %>%
  unique()

FACS_ID %>%
  group_by(user_id, date_taken, score) %>%
  ggplot(aes(x = date_taken,
             y = score,
             color = user_id)) +
  geom_point(size = 1) +
  facet_wrap( ~ user_id) +
  xlab("Date") +
  ylab("Score")
```

```{r FACS-number-of-times-taken, echo = FALSE}
# This looks at the number of times FACS is taken
# on average by customers
FACS_ID %>%
  group_by(user_id) %>%
  tally() %>%
  summarize(mean_count = mean(n)) %>%
  kable("html") %>%
  kable_styling()
  
```

```{r FACS-average-score, echo = FALSE}
FACS_ID %>%
  group_by(training) %>%
  summarize(mean_score = mean(score)) %>%
  kable("html") %>%
  kable_styling()
```

```{r combine-two-dataframes-FACS-and-data, echo = FALSE}
# I changed the name of the column names using
# names(df)[names(df) == 'old.var.name'] <- 'new.var.name'
names(data)[names(data) == 'Email'] <- 'user_email'

total_FACS <- merge(FACS_ID, data, by = "user_email")
```

## Training History of Tools: SETT
```{r SETT, echo = FALSE}
# This looks at the trend of training tool score
# by customer for SETT
SETT_ID <- use_SETT %>%
  group_by(user_id) %>%
  unique()

SETT_ID %>%
  group_by(user_id, date_taken, score) %>%
  ggplot(aes(x = date_taken,
             y = score,
             color = user_id)) +
  geom_point(size = 1) +
  xlab("Date") +
  ylab("Score")
```

```{r SETT-number-of-times-taken, echo = FALSE}
# This looks at the number of times SETT is taken
# on average by customers
SETT_ID %>%
  group_by(user_id) %>%
  tally() %>%
  summarize(mean_count = mean(n)) %>%
  kable("html") %>%
  kable_styling()
  
```

```{r SETT-average-score, echo = FALSE}
SETT_ID %>%
  group_by(training) %>%
  summarize(mean_score = mean(score)) %>%
  kable("html") %>%
  kable_styling()
```

```{r combine-two-dataframes-SETT-and-data, echo = FALSE}
# I changed the name of the column names using
# names(df)[names(df) == 'old.var.name'] <- 'new.var.name'
total_SETT <- merge(SETT_ID, data, by = "user_email")
```

## Training History of Tools: METT
```{r METT, echo = FALSE}
# This looks at the trend of training tool score
# by customer for METT

# I bloody FINALLY converted these bloody METT
# dates to the right freaking format. I am now
# 500 years old. Here is the link that finally
# bequeathed me the freaking knowledged that set
# me free from the bloody chains of date format
# conversion:
#https://stackoverflow.com/questions/20428862/identify-date-format-in-r-before-converting
use_METT$date_taken <- gsub("[0-9]{2}([0-9]{2})$", "\\1", use_METT$date_taken)
use_METT$date_taken <- as.Date(use_METT$date_taken, format = "%m/%d/%y")

METT_ID <- use_METT %>%
  group_by(user_id) %>%
  unique()

METT_ID %>%
  group_by(user_id, date_taken, score) %>%
  ggplot(aes(x = date_taken,
             y = score,
             color = user_id)) +
  geom_point(size = 1) +
  xlab("Date") +
  ylab("Score")
```

```{r METT-number-of-times-taken, echo = FALSE}
# This looks at the number of times METT is taken
# on average by customers
METT_ID %>%
  group_by(user_id) %>%
  tally() %>%
  summarize(mean_count = mean(n)) %>%
  kable("html") %>%
  kable_styling()
  
```

```{r METT-average-score, echo = FALSE}
METT_ID %>%
  group_by(training) %>%
  summarize(mean_score = mean(score)) %>%
  kable("html") %>%
  kable_styling()
```

```{r combine-two-dataframes-METT-and-data, echo = FALSE}
# I changed the name of the column names using
# names(df)[names(df) == 'old.var.name'] <- 'new.var.name'
total_METT <- merge(METT_ID, data, by = "user_email")
```

## Trends Across all Tools
```{r percent-answered, echo = FALSE}
Age <- total_tools %>%
  group_by(Age) %>%
  tally()

Sex <- total_tools %>%
  group_by(Sex) %>%
  tally()

Occupation <- total_tools %>%
  group_by(Occupation) %>%
  tally()

Age["Total" ,] <- colSums(Age)

print("For Age, 81.5% of people answered.")
print("For Sex, 84.6% of people answered.")
print("For Occupation, 92.2% of people answered.")
```

```{r combine-all-dataframes, echo = FALSE}
# I changed the name of the column names using
# names(df)[names(df) == 'old.var.name'] <- 'new.var.name'
FACS_METT <- rbind.fill(FACS_ID, METT_ID)

FACS_METT_SETT <- rbind.fill(FACS_METT, SETT_ID)

total_tools <- merge(FACS_METT_SETT, data, by = "user_email")
```
**Note:** This shows the score distribution of FACS.

```{r score-distribution-for-SETT, echo = FALSE}
total_tools %>%
  filter(training == "Subtle Expressions Training Tool") %>%
  group_by(score) %>%
  tally() %>%
  ggplot(aes(x = score,
             y = n,
             fill = score)) +
  geom_col(position = "dodge")
  
```
**Note:** This shows the score distribution of SETT.

```{r score-distribution-for-METT, echo = FALSE}
total_tools %>%
  filter(training == "Micro Expressions Training Tool") %>%
  group_by(score) %>%
  tally() %>%
  ggplot(aes(x = score,
             y = n,
             fill = score)) +
  geom_col(position = "dodge")
  
```
**Note:** This shows the score distribution of METT.

```{r our-customer-base-by-occupation, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(Sex != "") %>%
  filter(Occupation != "") %>%
  group_by(Occupation) %>%
  tally() %>%
  ggplot(aes(x = Occupation,
             y = n,
             fill = Occupation)) +
  geom_col(position = "dodge") +
  xlab("Occupation") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by occupation.

```{r our-customer-base-by-sex, echo = FALSE}
total_tools %>%
  filter(Sex != "") %>%
  group_by(Sex) %>%
  tally() %>%
  ggplot(aes(x = Sex,
             y = n,
             fill = Sex)) +
  geom_col(position = "dodge") +
  xlab("Sex") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by sex.

```{r our-customer-base-by-occupation-by-sex, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(Sex != "") %>%
  filter(Occupation != "") %>%
  group_by(Occupation, Sex) %>%
  tally() %>%
  ggplot(aes(x = Occupation,
             y = n,
             fill = Occupation)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Sex) +
  xlab("Occupation") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by occupation divided by sex.

```{r our-customer-base-by-sex-by-occupation, fig.height = 10, fig.width = 13, echo = FALSE}
total_tools %>%
  filter(Sex != "") %>%
  filter(Occupation != "") %>%
  group_by(Occupation, Sex) %>%
  tally() %>%
  ggplot(aes(x = Sex,
             y = n,
             fill = Sex)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Occupation) +
  xlab("Sex") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by sex divided by occupation.

```{r our-customer-base-by-age, echo = FALSE}
total_tools %>%
  filter(Age != "0") %>%
  group_by(Age) %>%
  tally() %>%
  ggplot(aes(x = Age,
             y = n,
             fill = Age)) +
  geom_col(position = "dodge") +
  xlab("Age") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by age.

```{r our-customer-base-by-age-by-sex, echo = FALSE}
total_tools %>%
  filter(Age != "0") %>%
  filter(Sex != "") %>%
  group_by(Sex, Age) %>%
  tally() %>%
  ggplot(aes(x = Age,
             y = n,
             fill = Age)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Sex) +
  xlab("Age") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by age divided by sex.

```{r our-customer-base-by-age-by-occupation, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(Age != "0") %>%
  filter(Sex != "") %>%
  group_by(Age, Occupation, Sex) %>%
  tally() %>%
  ggplot(aes(x = Age,
             y = n,
             fill = Sex)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Occupation) +
  xlab("Age") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by age divided by occupation.

```{r our-customer-base-by-referral, echo = FALSE}
# I had to go into Excel and do find and replace
# searches (a lot of them) in order to clean up
# and compile this data into broader categories. 

# I had to completely redo the entire column of
# How did you hear about us because of the inconsistent
# free response answers. I went into Excel and
# made the changes there because after trying to do
# revalue(df$column.name, c("B"="b")) I cried.

# I used the following script to condense the data
# and then figure out which ones I should be seeing
# in my graph.
#total_tools %>%
#  group_by(How.did.you.hear.about.us.) %>%
#  tally() %>%
#  kable("html") %>%
#  kable_styling()

# When cleaning data in excel I used the find
# function but with wildcards so *x* so that
# everything in the cell would be replaced by
# whatever I put in the replace function. 

total_tools %>%
  group_by(How.did.you.hear.about.us.) %>%
  tally() %>%
  filter(n > 40) %>%
  filter(How.did.you.hear.about.us. != "") %>%
  filter(How.did.you.hear.about.us. != ".") %>%
  ggplot(aes(x = How.did.you.hear.about.us.,
             y = n,
             fill = How.did.you.hear.about.us.)) +
  geom_col(position = "dodge") +
  xlab("How Did You Hear About Us") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows our customer base by how they heard about us.
**Word of Mouth/Previous Member:** These people were either referred by someone they know/it was recommended to them, were previous members, were referred by members of the site, by Asbury, by Chris Hadnagy, or one of our bulk buyers. 
**Educational Sphere:** This means they learned about us through a class, a lecture, through personal interest and research, professors, classmates, etc - anything related to education.

```{r how-you-heard-about-us-2-year-increments, echo = FALSE}
#total_tools %>%
#  group_by(How.did.you.hear.about.us.) %>%
#  tally() %>%
#  filter(n > 40) %>%
#  filter(How.did.you.hear.about.us. != "") %>%
#  filter(How.did.you.hear.about.us. != ".") %>%
#  ggplot(aes(x = How.did.you.hear.about.us.,
#             y = n,
#             fill = How.did.you.hear.about.us.)) +
#  geom_col(position = "dodge") +
#  xlab("How Did You Hear About Us") +
#  ylab("Number of Users") +
#  theme(axis.text.x =
#          element_text(angle = 90,
#                       hjust = 1))
```

```{r referral-by-occupation, fig.height = 10, fig.width = 13, echo = FALSE}
total_tools %>%
#  filter(user_email != "zoe.terrapon@club-internet.fr") %>%
#  filter(user_email != "malavasi_eleonora@libero.it") %>%
  group_by(How.did.you.hear.about.us., Occupation) %>%
  tally() %>%
  filter(n > 40) %>%
  filter(How.did.you.hear.about.us. != "") %>%
  filter(How.did.you.hear.about.us. != ".") %>%
  ggplot(aes(x = How.did.you.hear.about.us.,
             y = n,
             fill = How.did.you.hear.about.us.)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Occupation) +
  xlab("How Did You Hear About Us") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows referral by occupation. 

```{r referral-by-training-tool, fig.height = 10, fig.width = 13, echo = FALSE}
total_tools %>%
  group_by(How.did.you.hear.about.us., training) %>%
  tally() %>%
  filter(n > 40) %>%
  filter(How.did.you.hear.about.us. != "") %>%
  filter(How.did.you.hear.about.us. != ".") %>%
  ggplot(aes(x = How.did.you.hear.about.us.,
             y = n,
             fill = How.did.you.hear.about.us.)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ training) +
  xlab("How Did You Hear About Us") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```
**Note:** This shows referral by training tool. 

```{r score-by-occupation, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(training != "FACS Test") %>%
  filter(Occupation != "") %>%
  group_by(Occupation, score) %>%
  tally() %>%
  ggplot(aes(x = score,
             y = n,
             fill = score)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ Occupation) +
  xlab("Score") +
  ylab("Number of Users") +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1))
```

```{r top-performers-in-METT-and-SETT, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(score == 100.00000) %>%
  filter(Occupation != "") %>%
  group_by(training, Occupation) %>%
  tally() %>%
  ggplot(aes(x = Occupation,
             y = n,
             fill = Occupation)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ training) +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1)) +
  xlab("Occupation") +
  ylab("Number of Users")
```
**Note:** This shows our customer base in terms of top performers (score = 100) by occupation divided by METT vs SETT.

```{r top-performers-by-age, fig.height = 10, fig.width = 10, echo = FALSE}
total_tools %>%
  filter(score == 100.00000) %>%
  filter(Age != "0") %>%
  group_by(training, Age) %>%
  tally() %>%
  ggplot(aes(x = Age,
             y = n,
             fill = Age)) +
  geom_col(position = "dodge") +
  facet_wrap( ~ training) +
  theme(axis.text.x =
          element_text(angle = 90,
                       hjust = 1)) +
  xlab("Age") +
  ylab("Number of Users")
```
**Note:** This shows our customer base in terms of top performers (score = 100) by age divided by METT vs SETT.

```{r score-distribution-by-training, echo = FALSE}
#total_tools %>%

```















